\documentclass[11pt,notitlepage]{article}
\usepackage{graphicx}
\usepackage{amsmath}            % adds more math symbols
\usepackage{amssymb}
\usepackage[usenames,dvipsnames]{color}
\usepackage{multicol}
\usepackage{listings}
\title{LING-300: Homework 13}
\author{Leo Przybylski\\
\texttt{przybyls@arizona.edu}}

\newcommand{\question}[2]{\textbf{#1.} #2}
\newcommand{\subquestion}[2]{\par\hspace{0.5cm} \textbf{#1)} #2}
\newenvironment{answer}{\endpar%

}

    % Give wider margins; gives more text per page.

\setlength{\topmargin}{0.00in}
\setlength{\textheight}{8.75in}
\setlength{\textwidth}{6.625in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}

\setlength{\parindent}{0.0cm}	% Don't indent the paragraphs
%\setlength{\parskip}{0.4cm}	% distance between paragraphs

\definecolor{ubergray}{RGB}{245,245,245}
\begin{document}
  \maketitle
  {\setlength{\baselineskip}%
           {0.0\baselineskip}
  \section*{Carnie Chapter 11}
  \hrulefill \par}
\question{6}{IRISH}
\begin{quote}
[Data Analysis; Advanced]
Irish has a number of different complementizer forms. In declarative
clauses (statements), it uses the complementizer go/gur. As discussed
in the text above, when there is a question, this complementizer
switches to the wh form aL. (The idea behind this problem set is taken
from McCloskey 1979.)
\end{quote}

\subquestion{a}{Ceapann tú go bhuailfidh an píobaire an t-amhrán think you that play.FUT the piper the song "You think that the piper will play the song."}
\subquestion{b}{Caidé aL cheapann tú aL bhuailfidh an píobaire? What
  WH think you WH play.FUT the piper "What do you think the piper will
  play?"}
\begin{quote}
Note carefully the number of aL complementizers in sentence (b). (b)
pro- vides evidence that wh-phrases stop off in intermediate
specifiers of CP (for MLC reasons). Explain why. You need to make the
assumption that the complementizer aL only shows up when a wh-phrase
has at one point shown up in its specifier.
\end{quote}

\newpage
  {\setlength{\baselineskip}%
           {0.0\baselineskip}
  \section*{Notes and Instructor Comments}
  \hrulefill \par}
\end{document}
